Casting doubt on the causal link between intelligence and age at first intercourse:\\ A cross-generational sibling comparison design using the NLSY

### 2016-09-24 Manuscript/Manuscript.tex
update

\usepackage{alltt}
\usepackage{../Common/style/Mason}
\usepackage{listings}
\usepackage{inconsolata}
\usepackage[bottom]{footmisc} %fix footnotes
\usepackage{lineno}
\usepackage{adjustbox}
%\linenumbers
\interfootnotelinepenalty=10000
%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Casting doubt on the causal link between intelligence and age at first intercourse:\\ A cross-generational sibling comparison design using the NLSY}
\shorttitle{Intelligence and AFI}
%
% Authors and Affiliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}
%
% Author Note
\authornote{\input{../Common/content/title/authornote.tex}}
%
% Abstract
\abstract{%Last compiled \today\ at \currenttime\\
\input{../Common/content/title/abstract_empreport.txt}}
%
% Key Words
\keywords{Age at first intercourse; Cross-sectional Data; Discordant Sibling Design; Intelligence; Quasi-Experimental; Siblings}
%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\maketitle

@@

\subsubsection{Intelligence} Cousin differences in intelligence as assessed at ages 9.5, 10.5, and 11.5 were correlated using three different linking methods (Mixed, Daughters, Sons). Reliabilities across linking methods was consistent and high (min r = .86; max r = .95). However, we could not estimate test-retest reliabilities for Generation 1; we calculated the reliability using Lord's (\citeyear{Lord1963}) equation. The calculated reliability of Generation 1's differences in AFQT was 0.70, which was marginally acceptable, and obviously lower than the empirical correlation we derived for cousin differences.%0.7

%%%%%%%%%%%% Results %%%%%%%%%%%%
\section{Results}
\input{../Common/content/writing/results.tex}
%
% Between-Family
\subsection{Between-Family Analyses}
\input{../Common/content/writing/results_between.tex}

@@

\end{document}

>>>>

\usepackage{alltt}
\usepackage{../Common/style/Mason}
\usepackage{listings}
\usepackage{inconsolata}
\usepackage[bottom]{footmisc} %fix footnotes
\usepackage{lineno}
\usepackage{adjustbox}
\def\hyph{-\penalty0\hskip0pt\relax}  % trick hyphen
%\linenumbers
\interfootnotelinepenalty=10000
%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Casting doubt on the causal link between intelligence and age at first intercourse:\\ A cross-generational sibling comparison design using the NLSY}
\shorttitle{Intelligence and AFI}
%
% Authors and Affiliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}
%
% Author Note
\authornote{\input{../Common/content/title/authornote.tex}}
%
% Abstract
\abstract{%Last compiled \today\ at \currenttime\\
\input{../Common/content/title/abstract_empreport.txt}}
%
% Key Words
\keywords{Age at first intercourse; Cross-sectional Data; Discordant Sibling Design; Intelligence; Quasi-Experimental; Siblings}
%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\maketitle

@@

\subsubsection{Intelligence} Cousin differences in intelligence as assessed at ages 9.5, 10.5, and 11.5 were correlated using three different linking methods (Mixed, Daughters, Sons). Reliabilities across linking methods was consistent and high (min r = .86; max r = .95). However, we could not estimate test-retest reliabilities for Generation 1; we calculated the reliability using Lord's (\citeyear{Lord1963}) equation. The calculated reliability of Generation 1's differences in AFQT was 0.70, which was marginally acceptable, and obviously lower than the empirical correlation we derived for cousin differences.%0.7
%\vspace{-.2cm}
%%%%%%%%%%%% Results %%%%%%%%%%%%
\section{Results}
%\vspace{-.2cm}
\input{../Common/content/writing/results.tex}
%
% Between-Family
%\vspace{-.2cm}
\subsection{Between-Family Analyses}
%\vspace{-.2cm}
\input{../Common/content/writing/results_between.tex}

@@

  \section{Correlations}\label{appencor}  
\noindent
\captionof{table}{Zero-Order Correlations}\label{table_cor}
\begin{center}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=1\textwidth]{figure/reviewer2_cor-1}

\end{knitrout}
\end{center}\pagebreak

\noindent\begin{minipage}{\textwidth}

\begin{longtable}{@{\extracolsep{5pt}}rlll} \caption{\small Semi-Partial Correlations for Between-Family Joint Model, Predicting Gen2 Averages of AFI}\label{table_spcor_btw}
\hline
&   \multicolumn{3}{c}{Semi-Partial Correlation (p-value)}\\
Predictor &  \multicolumn{1}{c}{Mixed} & \multicolumn{1}{c}{Daughters} & \multicolumn{1}{c}{Sons}\\	
\hline 
Gen1 Mean Intel & 0.25 (<.0001)& 0.27 (<.0001)& 0.272 (<.0001)\\ 
Gen2 Mean Intel & \ensuremath{-0.003} (0.96) & 0 (0.997)& \ensuremath{-0.02} (0.73)\\ 
\hline\\
\textit{Notes:}  & \multicolumn{3}{r}{\parbox{.6\linewidth}{\footnotesize Joint Model is in Table \ref{table_Mean_Joint_Intelligence_Mean_Child_AFI_9}. The semi-partial correlation of Gen2 Mean AFI with each variable controls for all other variables in the table.}} \\ 
\end{longtable}
\end{minipage}
\vspace*{2cm}

\noindent\begin{minipage}{\textwidth}
\begin{longtable}{@{\extracolsep{5pt}}rlll} \caption{\small Pairwise Semi-Partial Correlations for Within-Family Joint Model, Predicting Gen2 Differences in AFI}\label{table_spcor_wtn}
\hline
&   \multicolumn{3}{c}{Semi-Partial Correlation (p-value)}\\
Predictor &  \multicolumn{1}{c}{Mixed} & \multicolumn{1}{c}{Daughters} & \multicolumn{1}{c}{Sons}\\	
\hline 
Gen2 Mean AFI & 0.29 (<.0001) & 0.29 (<.0001)& 0.36 (<.0001)\\ 
Gen2 Mean Intel & -0.075 (0.21) & -0.075 (0.21)& -0.081 (0.22)\\
Gen1 Mean Intel & 0.013 (0.83) & 0.013 (0.83)& -0.089 (0.18)\\ 
Gen2 Dif Intel & 0.06 (0.31) & 0.06 (0.31)& 0.018 (0.79)\\ 
Gen1 Dif Intel & 0.021 (0.73) & 0.021 (0.73)& 0.016 (0.81)\\ 
\hline\\
\textit{Notes:}  & \multicolumn{3}{r}{\parbox{.6\linewidth}{\footnotesize Joint Model is in Table \ref{table_Dif_Joint_Intelligence_Dif_Child_AFI_9}. The semi-partial correlation of Gen2 differences in AFI with each variable controls for all other variables in the table.}} \\ 
\end{longtable}\end{minipage}\\
\end{document}

### 2016-09-24 Manuscript/highlights.Rnw
update

\item Although ``Smart Teens Don't Have Sex (or Kiss Much Either)'' (Halpern \textit{et al}, 2000) at a descriptive level, the specific and proximal causal factors do not appear to be much related to smartness.

>>>>

\item Although ``smart teens don't have sex (or kiss much either)'' (Halpern \textit{et al}, 2000) at a descriptive level, their reasons for delaying these activities do not appear to be caused by their smartness.
